---
title: 'analysis 1 of n'
author: '{{your name(s)}}'
date: '`r Sys.Date()`'
editor_options: 
  chunk_output_type: console
---

I Recomend using [this](http://www.sthda.com/english/articles/24-ggpubr-publication-ready-plots/) library over the normal `ggplot2`.
I think it is easier.

# Setup

```{r}
library(dplyr)
library(ggpubr)

rm(list = ls())
options(scipen = 999)
```

# Generate some data

```{r}
seed <- 1234

set.seed(seed)
data <-
  data.frame(
    sex = factor(rep(c("F", "M"), each=200)),
    weight = c(rnorm(200, 55), rnorm(200, 58)))

sumary_data <-
  data %>%
  group_by(sex) %>%
  summarise(
    mean = mean(weight),
    sd = sd(weight)) %>%
  as.data.frame()
```

# Make a plot

Consider using only one formating style (`ggpar()`) for every figure in your project.

```{r}
figure <-
  data %>%
  ggdensity(
    x = "weight",
    add = "mean",
    color = "sex",
    fill = "sex") %>%
  ggpar(
    palette = 'Dark',
    xlab = 'Weight in KG',
    ylab = 'Density',
    legend = 'right',
    legend.title = 'Sex')

plot(figure)
```

# Save results

You can save more than one varable in a single file.
Images myst be saved in their own individual files.
Remember to save files with the same name as the script to preserve data linage

```{r}
figure %>%
  ggsave(
    '../results/analysis_1_of_n.jpg',
    plot = .,
    width = 6, height = 4.5, dpi = 300, units = 'in')

save(
  seed,
  sumary_data,
  file = '../results/analysis_1_of_n.RData')
```


